From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-02 paper.tex
Tide feedback

The core of the Blue Brain visualization infrastructure are multiple
high-resolution tiled display walls driven by our Tide software~\cite{tide}. All
walls are equipped with a multitouch user interface and can be remote controlled
from any web browser. The walls are build using thin-bezel, 55 inch, Full HD LCD
panels with a hardened glass sheet. We use $4\times 3$ and $3\times 3$
configurations for a total of 24 and 18 Megapixel resolution, respectively. The
display size of over five meter diagonally (four meter for $3\times 3$) allows
team-size collaboration (up to ten people) or project-wide presentations (up to
a hundred people). \fig{fTDW} shows one wall during a project-wide presentation
with multiple interactive applications running remotely on the wall.

While there is substantial research on tiled display wall software~\cite{Sage,
Sage2, Omegalib, DK:11, JLMV:06, DisplayCluster}, we found that most solutions
where not ready production use in a $24\times 7$ unattained environment. For
this reason, we started with the TACC DisplayCluster open source
software~\cite{DisplayCluster}, which we incrementally refactored and improved
to the current TIDE implementation. On the other hand, the hardware has been
commoditized to make these type of installations affordable to medium-sized
institutions which allowed us to build the software integration for a reasonable
startup cost. We have focused on the multitouch user interface, which implements
a low entry barrier for new users, a unique capability of our solution.

OpenDeck is our next-generation visualization system, aiming to integrate the
success of tiled display walls with a seamless transition to fully immersive
environments. We are currently in the process of installing a system which
consists of a semi-cylindrical back-projection screen with 41 Megapixel usable
resolution on a 36 $m^2$ surface (\fig{fOpenDeck}). Like the display walls, it
is equipped with multitouch capabilities which makes it usable as a monoscopic
collaboration system from the first day of installation. Unlike tiled display
walls, it is active stereo capable and equipped with a 3D tracking system for
immersive rendering. For increased immersion, a lower resolution front
projection system fills in the floor area. OpenDeck will run TIDA and our
immersive applications based on Equalizer~\cite{EMP:09} once the system is
installed.

OpenDeck will provide a unique environment for the research and development of
new visualization techniques. It will open a set of questions along immersive
touch user interfaces, transitions and mixing of monoscopic to immersive usage,
the combination of tracked and touch devices, multi-user immersion, latency for
remote immersive rendering as well as multi-site collaboration.

@@

Compared to other solutions~\cite{Sage,Sage2,DisplayCluster}, the development of
Tide was driven by the need of a stable and easy to use implementation. Tide
supports three types of content: files (high-resolution images, movies, pdfs),
built-in applications (web browser, whiteboard) and remote applications using
the Deflect library (DesktopStreamer, Equalizer-based applications, Brayns).
The multitouch user interface can handle multiple users manipulating different
windows and their content simultaneously.

>>>>

@@

While there is substantial research on tiled display wall software~\cite{Sage,
Sage2, Omegalib, DK:11, JLMV:06, DisplayCluster}, we found that most solutions
were not ready for production use in a $24\times 7$ unattended environment. For
this reason, we started with the TACC DisplayCluster open source
software~\cite{DisplayCluster}, which we incrementally refactored and improved
to the current TIDE implementation. On the other hand, the hardware has been
commoditized to make these type of installations affordable to medium-sized
institutions which allowed us to build the software integration for a reasonable
startup cost. We have focused on the multitouch user interface, which implements
a low entry barrier for new users, a unique capability of our solution.

Tide supports three types of content: files (high-resolution images, movies,
pdfs), built-in applications (web browser, whiteboard) and remote applications
using the Deflect library (DesktopStreamer, Equalizer-based applications,
Brayns). The multitouch user interface can handle multiple users manipulating
different windows and their content simultaneously.

The core of the Blue Brain visualization infrastructure are multiple
high-resolution tiled display walls driven by our Tide software~\cite{tide}. All
walls are equipped with a multitouch user interface and can be remote controlled
from any web browser. The walls are built using thin-bezel, 55 inch, Full HD LCD
panels with a hardened glass sheet. We use $4\times 3$ and $3\times 3$
configurations for a total of 24 and 18 Megapixel resolution, respectively. The
display size of over five meter diagonally (four meter for $3\times 3$) allows
team-size collaboration (up to ten people) or project-wide presentations (up to
a hundred people). \fig{fTDW} shows one wall during a project-wide presentation
with multiple interactive applications running remotely on the wall.

OpenDeck is our next-generation visualization system, aiming to integrate the
success of tiled display walls with a seamless transition to fully immersive
environments. We are currently in the process of installing a system which
consists of a semi-cylindrical back-projection screen with 41 Megapixel usable
resolution on a 36 $m^2$ surface (\fig{fOpenDeck}). Like the display walls, it
is equipped with multitouch capabilities which makes it usable as a monoscopic
collaboration system from the first day of installation. Unlike tiled display
walls, it is active stereo capable and equipped with a 3D tracking system for
immersive rendering. For increased immersion, a lower resolution front
projection system fills in the floor area. OpenDeck will run TIDE and our
immersive applications based on Equalizer~\cite{EMP:09} once the system is
installed.

OpenDeck will provide a unique environment for the research and development of
new visualization techniques. It will open a set of questions along immersive
touch user interfaces, transitions and mixing of monoscopic to immersive usage,
the combination of tracked and touch devices, multi-user immersion, latency
reduction for remote immersive rendering as well as multi-site collaboration.
